Epidemiological birth-death models with partner notification

### 2024-05-03 article/article.tex
Fixed lk calculations
REmoved unused code

In any of these scenarios, the notification must have happened after the partner tip branch start (as one of the model assumptions is that partners do not transmit after notification). Hence:
\begin{equation}
\scriptsize
l^{(n)}(i, r) = 0 \textit{\color{gray}~if $i$ is internal and $t_i > t_r$ or $i$ is a tip and $t_{parent(i)} > t_r$} \\
\label{eq:lp-zero}
\end{equation}

@@

We applied bdpn to each of the trees three times: fixing each of the BD parameters ($\lambda,\psi$ or $\rho$) to its real value (for identifiability).

>>>>

In any of these scenarios, the notification must have happened after the partner tip branch start (as one of the model assumptions is that partners do not transmit after notification). Hence:
\begin{equation}
\scriptsize
l^{(n)}(i, r) = 0 \textit{\color{gray}~if $t_i > t_r$} \\
\label{eq:lp-zero}
\end{equation}

@@

We applied bdpn to each of the trees fixing the sampling probability $\rho$ to its real value (for identifiability). The results with the becoming-uninfectious rate $\psi$ are similar and given in the Supplementary Material.
